Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-03-13 thesis/chapters/ch_chapter3.tex
updating reference

The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HWM2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}. This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HopkinsQuataertMurray2012}. We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.

>>>>

The log-normal distribution is found often in nature, generally describing multiplicative processes with non-negative values that grow with time. In astrophysics, for example, the log-normal distribution can be used to describe the time evolution of the star formation rate density \citep[see ][]{Gladders2013,Abramson2016,Diemer2017}. In addition, as expected from analytic theory \citep{Vazquez-Semadeni1994}, isothermal turbulence gives rise to log-normal density probability distribution functions \citep[PDFs;][]{Padoan1997, Passot1998, Ostriker1999,PadoanNordlund2002,KrumholzMcKee2005,Federrath2008}. Although these PDFs are only log-normal in simulations containing a more realistic, multi-phase ISM \citep{Scalo1998} if the disk is very stable \citep{WadaNorman2007}, individual phases within the ISM do exhibit some log-normality \citep{Tasker2009, Tasker2011,Joung2009,PriceFederrathBrunt2011, HQM2012}. It has been shown that the 3D density PDF and the column density PDF, in both simulations and observations, have a characteristic shape \citep{Vazquez-Semadeni1994,Burkhart2009, FederrathKlessen2013, Collins2012, Myers2015, Burkhart2017, Chen2018}. This includes a log-normal component, generated by multiplicative processes---in this case shocks and the turbulent cascade in the ISM---and a power-law component at high densities arising from the additive combination of individual, self-gravitating cloud structures .

@@

\section{Density PDF}
\label{appendix:density PDF}
We show the density PDF in Figure~\ref{fig:density_pdf} to illustrate our result in comparison to comparable works that have computed the density PDF in global galaxy simulations with a multi-phase ISM \citep{Joung2009, Tasker2009, Tasker2011, Tasker2015,HQM2012}. We show the mass-weighted PDF ($dm/Md\log n$) on the left, and the volume-weighted PDF ($dv/Vd\log n$) on the right. As has been demonstrated in previous work, the full density PDF (black) is not well described as a log-normal distribution. The mass-weighted PDF is broad and flat at low densities, with a large tail through to high densities.   The volume weighted PDF is much better described as a multi-component power law. The other phases do also show some log-normality (more for the mass weighted PDFs than the volume weighted PDFs), but all exhibit power-law tails towards higher densities. These deviations from a log-normal may still be the result of grouping together qualitatively different types of ISM gas.
